### 2024-05-31 Manuscript/main.tex
Update main.tex MWJ acknowledgements
Addedd ecol lett bits

\bigskip
\bigskip
\begin{center}

@@

@@

\end{center}
\bigskip
\noindent{*\bf Corresponding author.} \textit{t.guillerme@sheffield.ac.uk}\\ 
\vspace{1in}

%Line numbering
\modulolinenumbers[1]
\linenumbers

@@

\noindent (Keywords: )\\

@@

@@

\section{Repeatability and reproducibility}
The results figures and tables are entirely reproducible via \url{https://github.com/TGuillerme/eco_metrics_simulations}.

\section{Acknowledgements}
Thanks to Andrew Beckerman, Natalie Cooper, Alain Danet, Thomas Johnson and Gavin Thomas for comments on early versions of this manuscripts.\\
TG was funded by the UKRI-NERC grant NE/X016781/1.
SM was supported by NBFC, funded by the Italian Ministry of University and Research, PNRR, Missione 4, Componente 2, ``Dalla ricerca all'impresa'', Investimento 1.4, Project CN00000033.

>>>>

\bigskip
\begin{center}

@@

\noindent RH: The what how and why of trait-based analyses

@@

\end{center}
\bigskip
\noindent{*\bf Corresponding author.} \textit{t.guillerme@sheffield.ac.uk}\\

\noindent (Keywords: Functional diversity, dissimilarity, disparity, patterns, processes, mechanisms)\\

\begin{itemize}
   \item Article type: Letter
   \item Number of words in the abstract: @@@
   \item Number of words in the main text: @@@
   \item Number of words in the text box: @@@
   \item Number of references: @@@
   \item 3 Figures, 2 tables 1 text box @@@
\end{itemize}

\subsection{Statement of authorship}

TG, PC, MWJ, SM and TJM designed the study, analysed the data and wrote the manuscript. TG wrote the code to analyse the data.

\subsection{Data accessibility statement}

All code and data required to reproduce this analysis is available on @@@

@@

\newpage
%Line numbering
\modulolinenumbers[1]
\linenumbers

@@

\newpage

@@

\section{Repeatability and reproducibility}
The simulations, results figures and tables are entirely reproducible via \url{https://github.com/TGuillerme/eco_metrics_simulations}.

\section{Acknowledgements}
Thanks to Andrew Beckerman, Natalie Cooper, Alain Danet, Thomas Johnson and Gavin Thomas for comments on early versions of this manuscripts.
TG was funded by the UKRI-NERC grant NE/X016781/1.
SM was supported by NBFC, funded by the Italian Ministry of University and Research, PNRR, Missione 4, Componente 2, ``Dalla ricerca all'impresa'', Investimento 1.4, Project CN00000033.
MWJ was supported by NERC CENTA2 grant NE/S007350/1 and University of Birmingham.
